Satellite Alignments in Galaxy Pairs

### 2016-06-10 paper/ms.tex
papers de libeskind

>>>>

\citep{2011MNRAS.411.1525L} Measure the infall direction of satellites
in a DM only simulation of one pair of LG halos in a constrained
simulation. There is a definite infall direction but it's not
quantified in terms of the cosmic web.

\citep{2014MNRAS.443.1274L} Measure the infall direction of satellites
with respect to the V-web. They do it in a DM cosmological simulation
(64 Mpch, 1024 3 particles). They find that infall is done along the
e3 (i.e. filament) direction.

\citep{2015MNRAS.450.2727T} They measure the angle between satellites
and the direction defined by filaments (Bissous filament finder )to
find a signal both in SDSS and the semi-analytic galaxies in the
Millennium Simulation.

\citep{2015ApJ...799..212L} Detection of alignment of satellites along
the direction defined by filaments (velocity shear cosmic web) on the
SDSS DR7.

@ARTICLE{2014MNRAS.443.1274L,
   author = {{Libeskind}, N.~I. and {Knebe}, A. and {Hoffman}, Y. and {Gottl{\"o}ber}, S.
	},
    title = "{The universal nature of subhalo accretion}",
  journal = {\mnras},
archivePrefix = "arXiv",
   eprint = {1407.0394},
 keywords = {galaxies: haloes, cosmology: theory, dark matter, large-scale structure of Universe},
     year = 2014,
    month = sep,
   volume = 443,
    pages = {1274-1280},
      doi = {10.1093/mnras/stu1216},
   adsurl = {http://adsabs.harvard.edu/abs/2014MNRAS.443.1274L},
  adsnote = {Provided by the SAO/NASA Astrophysics Data System}
}
